\documentclass[12pt]{article}

\usepackage{amsmath,amssymb,amsfonts} %In case we need math stuff
\usepackage{graphicx} %For inserting images and stuff
\usepackage{listings} %For inserting code snippets
\usepackage{enumerate} %For fancy enumeration
\usepackage[margin=1.1cm]{geometry} %Nice margin setting

\title{ECSE 321 - Intro to Software Engineering\\Deliverable 6 Report}
\author{Harley Wiltzer\\Camilo Garcia La Rotta\\Jake Shnaidman\\Robert Attard\\Matthew Lesko}
\date{April 11, 2017}

\begin{document}
\pagenumbering{gobble} %No page number on title page
\maketitle
\newpage
\pagenumbering{arabic} %Arabic numeral page numbers on regular pages

\newpage
\textbf{1. Implementation}


\textbf{All the requirements formally identified by an ID are references to the Deliverable 1.}
\begin{itemize}

    \item \textbf{Functional:} Total implementation of the R. 1.1.1.1 to 1.1.1.4 with the caveat of serialization to text file instead of an xml format for the Web platform. This was a design choice made during the 2nd deliverable to use the same persistence methodology seen in Event Registration. R. 1.1.1.5 was not accomplished, a database was voted as too much of a frame for the access and retrieval of data. A much lightweight approach of storage in text files was preferred. R 1.1.1.6 is partially accomplished. Mobile and Desktop are fully capable of using each others xml outputs. Web remained incompatible due to its plain text output serialization.
        
	\item \textbf{Non-Functional:} From section R. 1.2.1 only R 1.2.1.3 will ship with the final
		report. All other requirements in this section were dropped from development as they related
		to an extra scheduling algorithm design that the team lacked time to develop.
	From section R. 1.2.2, all platforms provide a secure authentication procedure linked to a
	profile. The only requirement not achieved was 1.2.2.6, as NTRU cryptosystems required more
	research, and not enough time was available. From section 1.2.3 all requirements were achieved,
	providing a reliable cross platform version of the product was one of the main goals of the
	team. From section 1.2.4, all applications work under the same colour pallet, but as a caveat Mobile is
	the only platform without light/dark theme mode. It was chosen to rely on androids native
	accessibility options to change color gradients on the cellphone.
        

	\item \textbf{Desktop:} From section R 1.1.2 all but 1.1.2.9 was accomplished. As demanded by the client, the Desktop application is fully able to perform the tasks of an Instructor, Department and Student Profile which can be found in more depth in the Mobile and Web section of this report.
	
	\item \textbf{Web:} The web service is capable of dual profile actions. An administrator can log in and create courses instances and instructor profiles as well as linking them. An instructor can log in and publish job postings and manage the received applications as well as evaluating TAs.
    
	\item \textbf{Mobile:} The shipped application provides the capabilities of appying for a job,
		accepting/rejecting offers, creating and modifying the user's student profile, and viewing
		instructor evaluations. 
	   % \item 1.4.1 - The mobile application only allows student profiles to login
	   % \item 1.4.2 - The mobile application was written in java
	   % \item 1.4.3 - The mobile application only used libraries provided by android studio and no other tools were used
	   % \item 1.4.4 - The students may store their student ID in their description as a string.
	   % \item 1.4.5 - The application uses a controller to load job postings from persistence
	   % \item 1.4.6 - The application lists all the job postings to the user in a separate view
	   % \item 1.4.7 - This was not fulfilled since the administration can view other jobs that the student has applied for and can control whether or not he will get the job
	   % \item 1.4.8 - The user is not able to specify his preferences and rank his applications. He instead is given the choice to choose which offers he will ultimately accept
	   % \item 1.4.9 - The mobile application retrieves job offers from persistence
	   % \item 1.4.10 - The mobile application displays job offers to the user
	   % \item 1.4.11 - The student may accept or reject job offers

\end{itemize}

\textbf{2. Usability of Application}
%% -- The final state of the application, do all three platforms work as intended? Which Use Cases are each of the three applications capable of performing? Should the application be run in a certain way?

\begin{itemize}
	\item \textbf{Desktop:} The desktop program shall be run by double clicking on the .jar file of
		the program. All saved data (persistence data) is stored in the \$HOME/.tamas/output
		directory, which is generated by executing the init-desktop target of the build script. In
		order to run the desktop application, this persistence folder \textit{must} be created. Thus
		must only be done once, when using the app for the first time, and must be done subsequently
		any time the persistence folder has been deleted.
	\item \textbf{Web:} The Web application is accessed through the web and doesn't host any permanent or temporary files client-side. The user is required to access the server that hosts the website.
	
	\item \textbf{Mobile:} The mobile program shall be released as an apk file that may be installed
		on an Android phone. Once the apk file is installed, the user may use the application on the
		phone. Persistence from the desktop application may be imported into the mobile app by
		placing it in the mobile device's
		\texttt{/storage/emulated/0/Android/obb/ca.mcgill.ecse321.group10.TAMAS} directory.
\end{itemize}

\textbf{3. Testing of Applications}


%% -- Talk about the final state of testing. Have all unit tests been done -> Are we confident enough that certain inputs will not cause problems? Do they all pass? Coverage?
%% -- Is all integration testing done -> Are we confident enough with certain feaures working together? Are there any concerns for certain features? Will there be more testing in the future?
%% -- Is all system testing done -> Are we confident enough to release the product?
The unit, integration and system testing strategies devised for deliverable 3 were implemented for the desktop application to ensure that maximal performance and coverage as well as  to ensure proper functionality of the system would be achieved. The testing strategy needed to be adjusted somewhat for the web app due to the differnt way that each functionality was implemented in php. As the android app depended on the java code made for desktop, it was suficient to test units and integration on dekstop and not on android.
\begin{itemize}
		\item \textbf{Unit Testing:} 
		\begin{itemize}
			\item A plethora of unit tests were written for the desktop application, and currently offer 100\% coverage of the controller classes.
			\item  In similar fashion to the desktop unit tests, all controllers were tested seperately during unit tests for the web application. Coverage on the unit tests is similar to that of the desktop application.
		\end{itemize}
			\item \textbf{Integration Testing:} 
		\begin{itemize}
			\item Because the desktop app has more functionality than the web app, the integration testing of it involved a more comprehensive list of test cases than the desktop app did.
			\item As the web app only handles things from the perspective of a teachers point of view, which means to look at things in terms of jobs, it was sufficient to test that all functionality and error-detection involved in job creation was covered.
		\end{itemize}
	\item \textbf{System Testing:}At the system level, all three applications were extensively tested after each new iteration of the source code. Due to the sheer size of the applications, it is difficult to measure the exact system test coverage, though it is believed that the state coverage on all platforms was close to 100\%.
\end{itemize}

\textbf{4. Release Pipeline}


%% -- Ready for release or not?
%% -- Where and how shall it be released? Shall we release it as intended in the release plan?
The release pipeline shall follow the plan as in deliverable 4's report. Every release shall follow semantic versioning: MAJOR.MINOR.PATCH. With the first release being V1.0.0. During deployment, the Travis script shall invoke the scripts: ant export-desktop, ant export-web, and ant export-mobile. These shall export the necessary jar, apk, and web files. All source code shall be available as well.
\begin{itemize}
	\item \textbf{Desktop:} The Executable Desktop JAR archive shall be released. The APP/Desktop directory shall be available in the source code.
	\item \textbf{Web:} The Web Application zip archive shall be released. The APP/Web directory shall be available in the source code.
	\item \textbf{Mobile:} The apk file of the android program shall be released. The APP/Mobile directory shall be available in the source code.
\end{itemize}

It is interesting to note that a major part of the release pipeline time budget was allocated to the
implementation of build script. Apart from the base functionalities it is also capable of packaging
the web app and loading it in a browser, creating an executable and running the desktop application,
and installing the mobile app automatically to a connected android device. This strongly increased
the development team's productivity.\\

\textbf{5. Responsibilities for Each Phase}
\begin{itemize}
    \item \textbf{Harley Wiltzer: }%MVP
		%Sole developer of the Desktop application - designed the logic and UI for each
		%use case. Designed and implemented the multi-platform build script to completion. Principle
		%tester of the entire Desktop application.
    \item \textbf{Camilo Garcia: }
    \item \textbf{Jacob Shnaidman:(420+h) }
    \item \textbf{Robert Attard: 60+h}
    % Assisted in the development of the system architecture and tweaking of the webb application interface. Ensured that the unit and integration tests for web were up to date so that new features could be implemented. Co-designed the integration testing startegy for desktop and web. Assistenmd in system testing for the desktop app and was primary tester for the web application. Chose the color scheme for the web app.
    \item \textbf{Matthew Lesko: (60+h)} 
    % Involved in Design of Domain Model, Software Architecture, Use Case Diagram, and Behavioral Sequence Diagram. Updating necessary changes to Domain Model and Detailed Domain Model during this phase. Unit Testing Desktop application. Involved in implementing new Desktop application features under a Test Driven Development Paradigm. Involved in Deployment Phase of Software System. Suggested to use Travis CI as Deployment Tool and GitHub Releases as a release hosting solution. Implemented Travis CI as a CI tool.
\end{itemize}

\end{document}
